Adopting agile in the large: motivations, success factors and challenges

### 2013-01-25 tex/article.tex
Corrections

Agile methods have become an appealing alternative for companies striving to
improve their performance. Agile methods have been originally designed for small
and individual teams. This poses challenges when introducing agile to large
organizations where development teams can not be autonomous. We reviewed 30
experience reports and case studies describing the process of taking agile
methods into use in large organizations. The primary motive for agile adoption
is the need to improve performance. For a successful transformation the entire
organization must be aligned and all organizational units must participate.
Creating an agile communityin the organization will help the change to stick.
Typical problems are misunderstanding of the agile model, and difficulties
coordinating the agile teams.

@@

However, large organizations may have problems introducing agile methods
\citegen{Dyba2009}. As agile methods are initially designed for small teams
their application has proven to be problematic in a larger scale
\citegen{Boehm2005}. In a large organization development teams will need to
interface with other organizational units. As agile methods tend to focus on
inter-team practices which leaves it up to the organization to figure out how to
make agile work \citegen{Lindvall2004}.

@@

The goal of this research is to explore how and why large organizations adopt
agile methods. Studies on large scale agile transformations have been published,
but no extensive or summarizing research is available on the subject. In this
research we will give an overview of reported case studies on adopting agile
methods in large organizations. We will further discuss the motivations for
adopting agile methods, the characteristics of agile transformations, and
factors relating to success or challenge in the transformation process. Our
research is focused on the process of organizational change. We leave out topics
related to comparing the initial and transformed states of organizations, such
as measuring the performance of organizations before and after the
transformation.

@@

Introducing agile methods in large organizations is more difficult than it is in
small organizations \citegen{Dyba2008}. The difficulty is partly related to size
bringing higher organizational inertia which slows down organizational change
\citegen{Livermore2008}. Agile methods are not founded on the use of individual
tools or practices, but rather on a holistic way of thinking.
Adopting agile requires often change of the entire organizational culture
\citegen{Misra2010}.

One significant difference between small and large adoptions is that large
organizations have more dependencies between projects and teams. This increases
the need for formal documentation and thus reduces agility \citegen{Lindvall2004}.
In addition to inter-team coordination development teams are required to
interact with other organizational units, which are often non-agile of their
nature. For instance, HR may demand individuals to have strictly specified roles
in projects \citegen{Boehm2005}, or a change control board may inhibit use of
continuous integration or refactoring \citegen{Lindvall2004}. All units affected
by the agile transformation need to be informed and heard, and the agile process
must be adjusted according to their needs \citegen{Lindvall2004, Cohn2003,
Boehm2005}.

Agile methods will also affect management and business related functions. A key
challenge is that management must move away from life cycle models and towards
iterative and feature centric models \citegen{Nerur2005}. The focus must be
shifted from a large scale scope to shorter term project planning
\citegen{Misra2010}, as agile methods emphasize that planning is only meaningful
for the near future \citegen{Cohn2003}. However, the lack of planning can be a
concern as business and customer relationships often build on long term
roadmapping. Enabling operation with shorter term planning requires educating
stakeholders and reviewing contracting practices \citegen{Boehm2005}.

@@

The literature review was conducted as an application of Kitchenham's
method for systematic literature review (SLR) \citegen{Kitchenham2007}. The method
was applied to be performed by only one researcher, and to serve as a
preliminary work evaluating the feasibility of a more in-depth review.
Effort was limited by selecting only the following subset of SLR steps:
identification of primary studies, data extraction and synthesis. Steps left out
were the development of a systematic review protocol, strict study quality
assessment, and reviews in the study selection process.

The searches for primary studies was conducted in two steps. First a preliminary
search was made to sample the existing literature. Then a systematic search was
done based on the preliminary search. The following databases were included in
the searches: IEEExplore (http://ieeexplore.ieee.org/),
ACM (http://dl.acm.org/), Scopus (http://www.scopus.com/),
ProQuest \linebreak (http://search.proquest.com/).
Additionally the archive of International XP
Conference (http://link.springer.com/) was searched.

@@

The central role of management in the change was evident in many studies. This
was typically shown in that the change was initiated by the management and
management took responsibility of the change process. Several studies identified
a champion who was the driver of the change. Some studies reported the change to
be driven by external consultants or a cross organizational work group.

@@

The papers included in this study were mostly experience reports with no
research method. Some papers were of low quality, but they were included as our
aim was to give a view of the topic that is broader and inclined towards practice.

>>>>

Agile methods have become an appealing alternative for companies striving to
improve their performance, but they are originally designed for small and
individual teams. This poses challenges when introducing agile to large
organizations where development teams can not be autonomous. We reviewed 30
experience reports and case studies describing the process of taking agile
methods into use in large organizations. The primary motive for agile adoption
is the need to improve performance. For a successful transformation the entire
organization must be aligned and all organizational units must participate.
Creating an agile community in the organization will help the change to stick.
Typical problems are misunderstanding of the agile model, and difficulties
coordinating multiple agile teams.

@@

However, large organizations may have problems introducing agile methods
\citegen{Dyba2009}. As agile methods are initially designed for small teams
their application has proven to be problematic in a larger scale
\citegen{Boehm2005}. In a large organization development teams will need to
interface with other organizational units. Agile methods tend to focus on
intra-team practices, which leaves it up to the organization to figure out how to
tailor agile practices to suite a large organization \citegen{Lindvall2004}.

@@

The goal of this research is to explore how and why large organizations adopt
agile methods. Studies on large scale agile transformations have been published,
but no extensive or summarizing research is available on the subject. In this
paper we will give an overview of reported case studies on adopting agile
methods in large organizations. We will further discuss the motivations for
adopting agile methods, the characteristics of agile transformations, and
factors relating to success or challenge in the transformation process. Our
research is focused on the process of organizational change. We leave out topics
related to comparing the initial and transformed states of organizations, such
as measuring the performance of organizations before and after the
transformation.

@@

Introducing agile methods in large organizations is more difficult than it is in
small organizations \citegen{Dyba2008}. The difficulty is partly related to size
bringing higher organizational inertia which slows down organizational change
\citegen{Livermore2008}. Agile methods are not founded on the use of individual
tools or practices, but rather on a holistic way of thinking.
Adopting agile often requires change of the entire organizational culture
\citegen{Misra2010}.

One significant difference between small and large scale adoptions is that large
organizations have more dependencies between projects and teams. This increases
the need for formal documentation and thus reduces agility \citegen{Lindvall2004}.
In addition to inter-team coordination development teams are required to
interact with other organizational units, which are often non-agile in
nature. For instance, HR may demand individuals to have strictly specified roles
in projects \citegen{Boehm2005}, or a change control board may inhibit the use of
continuous integration or refactoring \citegen{Lindvall2004}. All units affected
by the agile transformation need to be informed and consulted, and the agile
process must be adjusted according to their needs \citegen{Lindvall2004,
Cohn2003, Boehm2005}.

Agile methods will also affect management and business related functions. A key
challenge is that management must move away from life-cycle models and towards
iterative and feature centric models \citegen{Nerur2005}. The focus must be
shifted from a large scale scope to shorter term project planning
\citegen{Misra2010}, as agile methods emphasize that planning is only meaningful
for the near future \citegen{Cohn2003}. However, the lack of planning can be a
concern as business and customer relationships often build on long term
roadmapping. Enabling operation with shorter term planning requires educating
stakeholders and reviewing contracting practices \citegen{Boehm2005}.

@@

The literature review was conducted as an application of Kitchenham's
method for systematic literature reviews (SLR) \citegen{Kitchenham2007}. The method
was applied to be performed by only one researcher, and to serve as a
preliminary work evaluating the feasibility of a more in-depth review.
Effort was limited by selecting only the following subset of SLR steps:
identification of primary studies, data extraction and synthesis. Steps left out
were the development of a systematic review protocol, strict study quality
assessment, and reviews in the study selection process.

The searches for primary studies was conducted in two steps. First a preliminary
search was made to sample the existing literature. Then a systematic search was
done based on the preliminary search. The following databases were included in
the searches: IEEExplore, ACM, Scopus, ProQuest. Additionally the archive of the
International XP was searched.

@@

The central role of management in the change was evident in many studies. This
was typically shown in that the change was initiated by the management and
management took responsibility of the change process. Several studies identified
a champion who was the driver for the change. Some studies reported the change to
be driven by external consultants or a cross organizational work group.

@@

The papers included in this study were mostly experience reports with no reported
research method. Some papers were of low quality, but they were included as our
aim was to give a view of the topic that is broader and inclined towards practice.
